### 2020-06-18 README.Rmd
Readied code for Dave inspection

* Permutation test:
  + Add line to that shuffles competitor species within `focal_and_comp` just before fitting model
  + permutation AND CV: add `run_shuffle` argument to `run_cv()`

@@

  # Focal vs comp main dataframe for analysis
  # Computed earlier
  load("focal_vs_comp_bw.Rdata")

@@

save(model_comp_tbl, file = "model_comp_tbl_4_shuffles.RData")
```

>>>>

Hey Dave! Start here!

**Repeat earlier code**:

```{r, eval = FALSE}
# Load packages ----------------------------------------------------------------
library(tidyverse)
library(forestecology)
library(snakecase)
library(skimr)
library(sf)
library(sfheaders)
# devtools::install_github("rvalavi/blockCV")
library(blockCV)
library(tictoc)
library(yardstick)
library(viridis)

# Load & preprocess data -------------------------------------------------------
# Read in census data from 2008 & 2014
bw_2008 <- 
  "https://deepblue.lib.umich.edu/data/downloads/z603qx485" %>% 
  read_delim(delim = "\t") %>% 
  mutate(spcode = to_any_case(spcode)) %>%
  select(
    treeID = treeid, stemID = stemtag, sp = spcode, quadrat, gx, gy, dbh, 
    date, codes
  )
bw_2014 <- 
  "https://deepblue.lib.umich.edu/data/downloads/1831ck00f" %>% 
  read_delim(delim = "\t") %>% 
  mutate(spcode = to_any_case(spcode)) %>%
  select(
    treeID = treeid, stemID = stemtag, sp = spcode, quadrat, gx, gy, dbh, 
    date, codes
  )

# Compute growth ---------------------------------------------------------------
census_df1 <- bw_2008
# we need to filter out the resprouts
census_df2 <- bw_2014 %>% 
  filter(!str_detect(codes, 'R'))
id <- "treeID"

bw_growth_df <- 
  # Merge both censuses and compute growth:
  compute_growth(census_df1, census_df2, id) %>% 
  mutate(sp = to_any_case(sp))

# Define buffers ---------------------------------------------------------------
cv_fold_size <- 100
max_dist <- 7.5

# Study region boundary polygon
bw_boundary <- bigwoods_study_region %>% 
  sf_polygon()

# Define spatial CV folds ------------------------------------------------------
set.seed(76)
bw_cv_grid <- spatialBlock(
  speciesData = bw_growth_df, theRange = 100, verbose = FALSE,
  # Some guess work in figuring this out:
  k = 28, xOffset = 0.5, yOffset = 0
)

**Loop through 4 scenarios of model fitting**:

@@

  # Focal vs comp main dataframe for analysis
  focal_vs_comp_bw <- bw_growth_df_orig %>% 
    create_focal_vs_comp(max_dist, model_specs = bw_specs, cv_grid = bw_cv_grid, id = "treeID")

@@

save(model_comp_tbl, file = str_c(format(Sys.time(), "%Y-%m-%d"), "_model_comp_tbl_99_shuffles.RData"))
```

**Plot results**:
